---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Ripc

<!-- badges: start -->
[![R-CMD-check](https://github.com/OCHA-DAP/Ripc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/OCHA-DAP/Ripc/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of Ripc is to provide access to [Integrated Food Security Phase
Classification](https://www.ipcinfo.org) (IPC) and
[Cadre Harmonisé](https://www.ipcinfo.org/ch/) (CH) data. 

## Installation

You can install the Ripc from CRAN:

```r
install.packages("Ripc")
```

The development version can be installed from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("OCHA-DAP/Ripc")
```

## Usage

Ripc provides functionality to access IPC data stored directly on the
[IPC-CH Public API](https://docs.api.ipcinfo.org). There are a wider set of
functions detailed further below, but most users will get the information they
need from the `ipc_get_population()` function which returns datasets of
country-level, group-level, and area-level analyses in a list.

```{r download, message = FALSE}
library(Ripc)

df_list <- ipc_get_population()
df_list$country
```

More details on the API are available below.

## IPC API

```{r child="vignettes/ipc-api.Rmd"}
```

## Help and issues

For any help, please file an issue on
[Github](https://github.com/OCHA-DAP/Ripc/issues).
