---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Ripc

<!-- badges: start -->
[![R-CMD-check](https://github.com/OCHA-DAP/Ripc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/OCHA-DAP/Ripc/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of Ripc is to provide access to [Integrated Food Security Phase
Classification](https://www.ipcinfo.org) (IPC) data. 

## Installation

You can install the Ripc like so:

``` r
# install.packages("remotes")
remotes::install_github("OCHA-DAP/Ripc")
```

The package is not currently available on CRAN.

## Usage

IPC data is stored on the [Humanitarian Data Exchange](https://data.humdata.org/dataset/ipc-country-data), and this package
provides a simple interface to pull this data directly. However, the data is
also stored in a format not readily usable for analysis or visualization. Thus,
this package also automatically wrangles the data into a format prepared for
analysis. This functionality is documented within `ipc_download()` and
`ipc_wrangle()` respectively.

For the user, all that is needed is a simple one liner.

```{r download, message = FALSE}
library(Ripc)

ipc_download()
```

## Help and issues

For any help, please file an issue on
[Github](https://github.com/OCHA-DAP/Ripc/issues). If the issue relates to
downloading the data from HDX, please refer to the [rhdx package](https://github.com/dickoa/rhdx).

